Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2019-08-10 man/figures/bai_cronos.Rmd
include color script

```{r load_pkg}
library("tidyverse")
library("here")
library("ggrepel")
library("scales")
library("grid")
library("gridExtra")
library("patchwork")
library("stringr")
library("pander")
library("lemon")
library("magrittr")
```

@@

# Lm CA-High
dfCaH <- cro_sites %>% 
  filter(year >= 1975) %>% 
  filter(site == 'CA-High')

@@

# Lm CA-Low 
dfCaL <- cro_sites %>% 
  filter(year >= 1975) %>% 
  filter(site == 'CA-Low')

@@

# Lm SJ
dfSJ <- cro_sites %>% 
  filter(year >= 1975) %>% 
  filter(site == 'SJ')

@@

```{r plot_configure}
# colores <- c("#B2DF8A","#1F78B4","#A6CEE3")
# colores <- c('#7570b3','#e7298a','#1b9e77')
# colores <- c('#33a02c', '#984ea3', '#a65628')
colores <- c("#000000", "#0072B2", "#D55E00") 
```

```{r plot_cronobai}
colores <- c("#B2DF8A","#1F78B4","#A6CEE3")
colores <- c("#000000", "#0072B2", "#D55E00")

# cores 
cronos_bai <- cro_sites %>% filter(nseries > 5) %>% 
  ggplot(aes(x=year, y=bai_mean/100, colour=site)) + 
  theme_bw() + ylab('BAI') + 
  geom_ribbon(aes(ymin = (bai_mean - bai_se)/100,
                  ymax = (bai_mean + bai_se)/100,
                  fill=site), alpha=.4, colour=NA) +
  geom_line() + 
  geom_point(size=.8) + 
  scale_colour_manual(values = colores) +
  scale_fill_manual(values = colores) +
  ylab(expression(paste("BAI (", cm^2, year^-1, ")", sep=''))) +
  scale_x_continuous(breaks = seq(1815, 2020, by=10), limits=c(1815,2020), sec.axis = dup_axis()) +
  geom_smooth(data = subset(cro_sites, year > 1975 & site == 'CA-High'), 
              aes(x=year, y=bai_mean/100, colour=site), method = 'lm', se=FALSE, size = .5) +
  geom_smooth(data = subset(cro_sites, year > 1975 & site == 'CA-Low'), 
              aes(x=year, y=bai_mean/100, colour=site), method = 'lm', se=FALSE, size = .5) +
  geom_smooth(data = subset(cro_sites, year > 1975 & site == 'SJ'), 
              aes(x=year, y=bai_mean/100, colour=site), method = 'lm', se=FALSE, size = .5)  +
  geom_text_repel(data = lms, 
                  aes(x=year, y = y, colour = site, label = labelp),
                  direction = "x", nudge_x = Inf, nudge_y = 1, show.legend = FALSE, 
                  size = 3) + 
  theme(panel.grid = element_blank(),
        axis.text.x=element_text(size=6),
        legend.position = c(0.2,.8),
        strip.background = element_blank(),
        axis.title.x.top = element_blank(), 
        axis.text.x.top = element_blank())  
```

```{r plot_samp}
  # scale_y_continuous(sec.axis = sec_axis(~ ., name = '# trees', breaks = c(0,15,30))) +
  # geom_line(aes(x=year, y=n_trees+40, colour=site)) 
samp <- cro_sites %>% ggplot(aes(x=year, y=n_trees, colour=site)) + 
  theme_bw() + ylab('# trees') + 
  geom_line() + 
  scale_colour_manual(values = colores) +
  scale_fill_manual(values = colores) +
  scale_x_continuous(breaks = seq(1815, 2020, by=10), limits=c(1815,2020), 
                     sec.axis = dup_axis(), position = "top") +
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title.x=element_blank(),
        axis.text.x.top = element_text(size=6), 
        axis.text.x.bottom = element_blank(), 
        # axis.text.x=element_blank(),
        # axis.ticks.x=element_blank(), 
        # plot.margin = margin(t = 5, r = 0, b = -5, l = 0, unit = "pt")
        ) 
  # theme(plot.margin = unit(c(1,5,-30,6),units="points"),
  #       axis.title.y = element_text(vjust =0.25))
```

@@

**Figure 4.** Basal Area Increment (BAI) chronologies of *Q. pyrenaica* for northern population (SJ; *orange*) and southern ones: low-elevation (CA-Low; *blue*) and high-elevation (CA-High, *black*) sites. Shading areas correspond to standard error of the mean. Number of series are displayed in the upper plot. We only show years replicated with # series > 5. Linear trends since 1975 are shown all sites (numbers indicate $r^2$ values; asterisks indicate significant linear trend, *p < 0.001*).

>>>>

```{r load_pkg}
library("tidyverse")
library("here")
library("ggrepel")
library("scales")
library("grid")
library("gridExtra")
library("patchwork")
library("stringr")
library("pander")
library("lemon")
library("magrittr")
source(here::here('/script/R/colores_den.R'))

@@

year_init <- 1975

# Lm CA-High
dfCaH <- cro_sites %>% 
  filter(year >= year_init) %>% 
  filter(site == 'CA-High')

@@

# Lm CA-Low 
dfCaL <- cro_sites %>% 
  filter(year >= year_init) %>% 
  filter(site == 'CA-Low')

@@

# Lm SJ
dfSJ <- cro_sites %>% 
  filter(year >= year_init) %>% 
  filter(site == 'SJ')

@@

```{r plot_configure}
# colores <- c("#B2DF8A","#1F78B4","#A6CEE3")
# colores <- c('#7570b3','#e7298a','#1b9e77')
# colores <- c('#33a02c', '#984ea3', '#a65628')
# colores <- c("#000000", "#0072B2", "#D55E00") 
# colores <- c("#B2DF8A","#1F78B4","#A6CEE3")
# colores <- c("#000000", "#0072B2", "#D55E00")

```{r plot_cronobai}

# cores 
cronos_bai <- cro_sites %>% filter(nseries > 5) %>% 
  ggplot(aes(x=year, y=bai_mean/100, colour=site)) + 
  theme_bw() + ylab('BAI') + 
  geom_ribbon(aes(ymin = (bai_mean - bai_se)/100,
                  ymax = (bai_mean + bai_se)/100,
                  fill=site), alpha=.4, colour=NA) +
  geom_line() + 
  geom_point(size=.8) + 
  scale_colour_manual(values = colores_den) +
  scale_fill_manual(values = colores_den) +
  ylab(expression(paste("BAI (", cm^2, year^-1, ")", sep=''))) +
  scale_x_continuous(breaks = seq(1815, 2020, by=10), limits=c(1815,2020), sec.axis = dup_axis()) +
  geom_smooth(data = subset(cro_sites, year > year_init & site == 'CA-High'), 
              aes(x=year, y=bai_mean/100, colour=site), method = 'lm', se=FALSE, size = .5) +
  geom_smooth(data = subset(cro_sites, year > year_init & site == 'CA-Low'), 
              aes(x=year, y=bai_mean/100, colour=site), method = 'lm', se=FALSE, size = .5) +
  geom_smooth(data = subset(cro_sites, year > year_init & site == 'SJ'), 
              aes(x=year, y=bai_mean/100, colour=site), method = 'lm', se=FALSE, size = .5)  +
  geom_text_repel(data = lms, 
                  aes(x=year, y = y, colour = site, label = labelp),
                  direction = "x", nudge_x = Inf, nudge_y = 1, show.legend = FALSE, 
                  size = 3) + 
  theme(panel.grid = element_blank(),
        axis.text.x=element_text(size=6),
        legend.position = c(0.2,.8),
        strip.background = element_blank(),
        axis.title.x.top = element_blank(), 
        axis.text.x.top = element_blank())  
```

```{r plot_samp}
  # scale_y_continuous(sec.axis = sec_axis(~ ., name = '# trees', breaks = c(0,15,30))) +
  # geom_line(aes(x=year, y=n_trees+40, colour=site)) 
samp <- cro_sites %>% ggplot(aes(x=year, y=n_trees, colour=site)) + 
  theme_bw() + ylab('# trees') + 
  geom_line() + 
  scale_colour_manual(values = colores_den) +
  scale_fill_manual(values = colores_den) +
  scale_x_continuous(breaks = seq(1815, 2020, by=10), limits=c(1815,2020), 
                     sec.axis = dup_axis(), position = "top") +
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title.x=element_blank(),
        axis.text.x.top = element_text(size=6), 
        axis.text.x.bottom = element_blank(), 
        # axis.text.x=element_blank(),
        # axis.ticks.x=element_blank(), 
        # plot.margin = margin(t = 5, r = 0, b = -5, l = 0, unit = "pt")
        ) 
  # theme(plot.margin = unit(c(1,5,-30,6),units="points"),
  #       axis.title.y = element_text(vjust =0.25))
```

@@

**Figure 4.** Basal Area Increment (BAI) chronologies of *Q. pyrenaica* for northern population (SJ; *red*) and southern ones: low-elevation (CA-Low; *green*) and high-elevation (CA-High, *blue*) sites. Shading areas correspond to standard error of the mean. Number of series is displayed in the upper plot. We only show years replicated with # series > 5. Linear trends since 1975 are shown all sites (numbers indicate $r^2$ values; asterisks indicate significant linear trend, *p < 0.001*).
